---
title: "R Package for T4RR S16"
author: "Schuyler"
date: "May 6, 2016"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{R Package for T4RR S16}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8](inputenc)
---

## binnit

Binnit is a function designed to split __BED format__ data into 'bins', or smaller subsamples, either of a designated size or proportion of the total size of the primary. BED format is used for genome data but may be applied to other datasets as well. BED format lists the chromosome in column 1 and the size of the chromosome in column 2.

* BED format

Chromosome  | Size
----------- | -------
1           | 3000
2           | 5000
3           | 2000


## How to run binnit

The first thing you need is a dataset in the correct format:

```{r echo=TRUE}
data <- data.frame("chromosome"=sequence(3), "size"=round(runif(3,5000000,50000000)))
data
```

With that dataset and the binnit function loaded into the R workspace the function can then be run.
```{R}
library(RSchuyler)
```


The function takes three arguments, the first being the BED format dataset. The second argument asks for intervals (TRUE|FALSE). When FALSE each chromosome will be split into bins of equal size, when TRUE then they will be split into bins of a given size. The third argument is the number of bins or nubmer of Megabases for each bin that's being created.

```{r echo=TRUE}
create.genome.intervals(chromosome.sizes=data, intervals=TRUE, size=5)
```
vs
```{r echo=TRUE}
create.genome.intervals(chromosome.sizes=data, intervals=FALSE, size=5)
```
